Gammapy: A Python package for gamma-ray astronomy

### 2023-05-25 src/ms-review.tex
Add links to online documentation, where more info is available

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and IRFs as well as functionality
to read the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps, are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages, respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets, for example, to compute a spectrum using data from several facilities. Estimator classes,
which are contained in \code{gammapy.estimators}, are used to
compute higher level science products such as flux and significance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high-level interface for executing analyses
defined from configuration files. In the following sections, we will
introduce all sub-packages and their functionalities in more detail.

@@

Some example IRFs read from public data files and plotted with \gammapy are shown 
in Figure~\ref{fig:irfs}.

@@

@@

@@

@@

@@

>>>>

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and IRFs as well as functionality
to read the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps, are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages, respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets, for example, to compute a spectrum using data from several facilities. Estimator classes,
which are contained in \code{gammapy.estimators}, are used to
compute higher level science products such as flux and significance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high-level interface for executing analyses
defined from configuration files. In the following sections, we will
introduce all sub-packages and their functionalities in more detail.
In the online documentation we also provide an overview of all
the \gammapy sub-packages\footnote[number]{\url{https://docs.gammapy.org/1.0/user-guide/package.html}}.

@@

Some example IRFs read from public data files and plotted with \gammapy are shown 
in Figure~\ref{fig:irfs}. More information on \code{gammapy.irf} can be found 
in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/user-guide/irf/index.html#irf}}.

@@

More information on the \code{gammapy.maps} sub-module can be found 
in the online documentation\footnote{\url{https://docs.gammapy.org/1.0/user-guide/maps/index.html#maps}}.

@@

We also refer to our online documentation for more details on \code{gammapy.datasets}
\footnote{\url{https://docs.gammapy.org/1.0.1/user-guide/datasets/index.html#datasets}}.

@@

More detailed information on the \code{gammapy.makers} sub-package is available online\footnote{\url{https://docs.gammapy.org/1.0/user-guide/makers/index.html#makers}}.

@@

Our online documentation provides more information on \code{gammapy.stats}
\footnote{\url{https://docs.gammapy.org/1.0/user-guide/stats/index.html#stats}}.

@@

More details on the \code{gammapy.estimators} sub-module are available online \footnote{\url{https://docs.gammapy.org/1.0/user-guide/estimators.html#estimators}}.
